---
title: "Power"
authors: Will and Alon
format: 
  html:
    code-fold: show
    toc: true
    number-sections: true
    embed-resources: true
editor: visual
execute:
  echo: true
  message: false
  warning: false
---

## Assignment 4

For this assignment write a new Quartro document based on the analysis of power required for different \*possible_cars\* from today's class

\* Add an additional super light car with mass 5,000 kg and a surface area 10m2

\* Compute the mean and maximum power for Cars A, B, C and for your new car, assuming that average highway speed is 80 km/hr with a standard deviation of 10km/hr;  Use 2 different methods to compute the mean and maximum power for each car type; a) \*\*FOR\*\* loop and b) the \*\*pmap\*\* function from \*\*purr\*\*

\* Create two boxplots (one for each method (\*\*FOR\*\* and \*\*pmap\*\*) that show the range of power consumption (across sampled speeds) for each car type.

```{r}
#libraries
library(tidyverse)
library(here)
library(purrr)
```

FOR LOOP

```{r}
#using for loop

```

PMAP

```{r}
possible_cars1 = data.frame


```
