---
title: "Power"
authors: Will and Alon
format: 
  html:
    code-fold: show
    toc: true
    number-sections: true
    embed-resources: true
editor: visual
execute:
  echo: true
  message: false
  warning: false
---

## Assignment 4

For this assignment write a new Quartro document based on the analysis of power required for different \*possible_cars\* from today's class

\* Add an additional super light car with mass 5,000 kg and a surface area 10m2

\* Compute the mean and maximum power for Cars A, B, C and for your new car, assuming that average highway speed is 80 km/hr with a standard deviation of 10km/hr;  Use 2 different methods to compute the mean and maximum power for each car type; a) \*\*FOR\*\* loop and b) the \*\*pmap\*\* function from \*\*purr\*\*

\* Create two boxplots (one for each method (\*\*FOR\*\* and \*\*pmap\*\*) that show the range of power consumption (across sampled speeds) for each car type.

```{r}
#libraries
library(tidyverse)
library(here)
library(purrr)
```

```{r}
#bring in the autopower function and define 'possible_cars'
source("../R/Auto_Power.R")
# generate a structure to store info on our possible cars
possible_cars = data.frame(name = c("A","B","C"),mass=c(10000,65000,38000), area = c(22,30,22))

# first look at how results vary for mean speed say 100km/hr
# do conversion
speed_base = 100 * 0.28

# because I have one mass and area for each car and only 1 speed
# I can estimate power for each car type
# add to the data structure
possible_cars$power = auto_power(V=speed_base, A = possible_cars$area, m=possible_cars$mass)

head(possible_cars)

# show results                         
ggplot(possible_cars, aes(x=mass, y=power, fill=as.factor(area)))+geom_col()+labs(y="Power W", x="Mass (kg)", fill="Area (m2)")
```

FOR LOOP

```{r}
#using for loop


```

PMAP

```{r}

```
