---
title: "Power"
authors: Will and Alon
format: 
  html:
    code-fold: show
    toc: true
    number-sections: true
    embed-resources: true
editor: visual
execute:
  echo: true
  message: false
  warning: false
---

## Assignment 4

For this assignment write a new Quartro document based on the analysis of power required for different \*possible_cars\* from today's class

\* Add an additional super light car with mass 5,000 kg and a surface area 10m2

\* Compute the mean and maximum power for Cars A, B, C and for your new car, assuming that average highway speed is 80 km/hr with a standard deviation of 10km/hr;  Use 2 different methods to compute the mean and maximum power for each car type; a) \*\*FOR\*\* loop and b) the \*\*pmap\*\* function from \*\*purr\*\*

\* Create two boxplots (one for each method (\*\*FOR\*\* and \*\*pmap\*\*) that show the range of power consumption (across sampled speeds) for each car type.

```{r}
#libraries
library(tidyverse)
library(here)
library(purrr)
library(patchwork)
```

```{r}
#bring in the autopower function and define 'possible_cars'
source("autopower.R")
# generate a structure to store info on our possible cars
possible_cars = data.frame(name = c("A","B","C", "D"),mass=c(10000,65000,38000,5000), area = c(22,30,22,10))

# first look at how results vary for mean speed say 100km/hr
# do conversion
speed_base = 80 
nsample = 200
speeds = rnorm(mean=speed_base, sd=10, n = nsample)
# because I have one mass and area for each car and only 1 speed
# I can estimate power for each car type
# add to the data structure
possible_cars$power = auto_power(V=speed_base, A = possible_cars$area, m=possible_cars$mass)

head(possible_cars)

# show results                         
ggplot(possible_cars, aes(x=mass, y=power, fill=as.factor(area)))+geom_col()+labs(y="Power W", x="Mass (kg)", fill="Area (m2)")
```

FOR LOOP

```{r}
# Create an empty data frame to store the power results
powerall2 <- as.data.frame(matrix(nrow = length(speeds), ncol = nrow(possible_cars)))

# Calculate power for each car using a FOR loop
for (i in 1:nrow(possible_cars)) {
  powerall2[, i] <- auto_power(A = possible_cars$area[i], m = possible_cars$mass[i], V = speeds)
}

# Assign column names to powerall2
colnames(powerall2) <- possible_cars$name

# Turn columns into rows for ggplot
powerallr2 <- powerall2 %>% pivot_longer(cols = everything(), names_to = "car", values_to = "power")

# View first few rows of reshaped data
head(powerallr2)

# Boxplot of power consumption using the FOR loop method
loop_plot <- ggplot(powerallr2, aes(car, power, fill = car)) + 
  geom_boxplot() + 
  ggtitle("For Loop")
loop_plot
```

PMAP

```{r}


# Use pmap to apply the auto_power function for each car
powerall3 <- pmap(list(A = possible_cars$area, m = possible_cars$mass), auto_power, V = speeds)

# Convert powerall3 to a data frame
powerall3 <- as.data.frame(powerall3)

# Assign column names to powerall3
colnames(powerall3) <- possible_cars$name

# Turn columns into rows for ggplot
powerallr3 <- powerall3 %>%
  pivot_longer(cols = everything(), names_to = "car", values_to = "power")

# View first few rows of reshaped data
head(powerallr3)

# Boxplot of power consumption using the pmap method
method3_plot <- ggplot(powerallr3, aes(car, power, fill = car)) + 
  geom_boxplot() + 
  ggtitle("pmap")
method3_plot

# ----------- Combine Plots -----------

# Combine both boxplots into one plot using patchwork
final_plot <- loop_plot + method3_plot
final_plot

```
